---
title: "Breast_Cancer_code_06"
author: "Nam, Yeong-jae"
date: "`r Sys.Date()`"
output: 
    prettydoc::html_pretty:
      theme: leonids
      toc: yes
---
***
필요패키지: `Hmisc`, `PerformanceAnalytics`, `ggplot2`, `GGally`, `corrplot`, `factoextra`, `gridExtra`, `caret`, `C50`, `highcharter`, `randomForest`


## 1. 양성과 악성 유방암에 대한 이항 분류 by Visualization
```{r}
## Loading and observing data

Cancer = read.csv(".\\data\\Breast_Cancer.csv")

head(Cancer)

dim(Cancer)
```

<br><br>


### 1-1. Null, missing value가 있는 열을 확인.
함수를 직접 만들어서 확인...
```{r}
## Function to print the columns with null value

CheckColAllNulls = if(ncol(Filter(function(x) any(is.na(x)), Cancer))>0) {
  cat("columns have nulls: ", ncol(Filter(function(x) any(is.na(x)), Cancer)))
  cat("\n\n")
  cat("columns names that have nulls: ", colnames(Filter(function(x) any(is.na(x)), Cancer)))
  cat("\n\n")
  # df = filter(function(x) ! any(is.na(x)), df)
  # print("columns having any nulls are removed")
} else{
  print("No columns having any nulls are found")
}

```
```{r}
table(Cancer$X)
```
```{r}
## Removing the column X

Cancer = Filter(function(x) ! any(is.na(x)), Cancer)

dim(Cancer)
```
<br><br>

### 1-2. 범주형 변수 인코딩
```{r}
## if diagnosis column is M meaning Malignant then 1 else 0 for B or Benign

Cancer$diagnosis = (ifelse(Cancer$diagnosis=='B', 0, 1))

table(Cancer$diagnosis)

Cancer$Label_Diagnosis = factor(ifelse(Cancer$diagnosis == 1, 1, 0))
```

<br><br>

### 1-3. 데이터 요약
```{r}
# summary(Cancer)
str(Cancer)

head(Cancer)
```

## 2. 변수간 상관관계
```{r}
library(Hmisc)

flattenCorrMatrix = function(cormat, pmat){
  ut = upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = colnames(cormat)[col(cormat)[ut]],
    cor = (cormat)[ut],
    p = pmat[ut]
  )
}

corr_res = rcorr(as.matrix(Cancer[,c(2:11)]))

flattenCorrMatrix(corr_res$r, corr_res$P)
```

<br><br>

```{r, warning=FALSE}
library(PerformanceAnalytics)
# showing histogram
# color grey

options(repr.plot.width=20, repr.plot.height=20, repr.plot.res=100)

chart.Correlation(Cancer[,c(2:11)], histogram=T,
                  col='grey10',
                  pch=1,
                  cex.cor.scale=2,
                  main="Cancer Correlation Plot",
                  cex.labels=20)
```

<br><br>

```{r}
library(ggplot2)
library(GGally)

options(repr.plot.width = 20,  repr.plot.height=15, repr.plot.res=100)

# The correlation plots should have 2 distributions of seperate colors according to out Label Diagnosis
# alpha is basically the opacity

ggpairs(Cancer[,c(3:11, 33)],
        aes(color=Label_Diagnosis, alpha=0.7),
        lower=list(combo=wrap("facethist", binwidth=0.5)),
        upper = list(continuous = wrap("cor", size=2))) +
  labs(title="Cancer Plot") + 
  theme(plot.title=element_text(face='bold', color='black', hjust=0.5, size=5))
```

```{r, warning=FALSE}
library(corrplot)

options(repr.plot.width = 20, repr.plot.height = 20, repr.plot.res = 100)

corrplot(cor(Cancer[,c(2:12)]),
         type='lower',
         order='hclust',
         tl.col='black',
         addCoef.col = 'black',
         number.cex = 0.8,
         tl.cex = 0.8,
         title="Cancer Mean",
         diag=F,
         mar=c(0,0,1,0))

corrplot(cor(Cancer[,c(12:22, 2)]),
         type='lower',
         order='hclust',
         tl.col='black',
         addCoef.col = 'black',
         number.cex = 0.8,
         tl.cex = 0.8,
         title="Cancer Worst",
         diag=F,
         mar=c(0,0,1,0))

corrplot(cor(Cancer[,c(22:32, 2)]),
         type='lower',
         order='hclust',
         tl.col='black',
         addCoef.col = 'black',
         number.cex = 0.8,
         tl.cex = 0.8,
         title="Cancer Worst",
         diag=F,
         mar=c(0,0,1,0))
```
```{r}
## Another library that could be usd: ggcorr

# ggcorr(Cancer[,c(2:11)], name="corr", label=T) + 
# theme(legend.position="none") +
# labs(title="Cancer Mean") +
# theme(plot.title=element_text(face='bold', color='black', hjust=0.5, size=12))
```

### 2-1. 요약
아래 변수들은 Diagnosis와 높은 상관성을 보인다.
* concavity_mean/concave.points_mean
* area_mean/radius_mean/perimeter_mean
* area_worst/radius_worst/perimeter_worst
* concavity_worst/concave.points_worst

## 3. PCA를 이용해서 변수 선택
```{r}
library(factoextra)

Cancer_pca = transform(Cancer)

all_pca = prcomp(Cancer_pca[,c(3:32)], cor=TRUE, scale=TRUE)

summary(all_pca)
```
PC1부터 PC6부터 전체변동의 88.7%를 설명.


<br><br>


```{r}
## Visualization of PCA components using screeplot -> 산비탈그림(PC 선택)


options(repr.plot.width = 20, repr.plot.height = 10, repr.plot.res = 100)

fviz_eig(all_pca,
         addlabels = TRUE,
         ylim=c(0, 100),
         geom=c("bar", "line"),
         barfill="pink",
         barcolor='grey',
         linecolor="red",
         ncp=10, labelsize=13, repel=T) +
  theme(text=element_text(size=25, color="#002b80"),
        axis.title=element_text(size=10),
        axis.text=element_text(size=10)) +
  labs(title="Cancer all variables PCA",
       x="Principal Components",
       y="% of variance explained")
```
```{r}
fviz_pca_var(all_pca, labelsize=3, repel=T) + 
  theme(text = element_text(size=3, color="#002b80"),
        axis.title = element_text(size=5),
        axis.text = element_text(size=3)) +
  labs(title ="Cancer all variavbles PCA\n",
       x="Dim2 (19%)",
       y="Dim1 (44%)")
```

```{r}
(all_var_explained = get_pca_var(all_pca))
```

```{r}
library(corrplot)

options(repr.plot.width = 20, repr.plot.height = 15)

corrplot(all_var_explained$contrib,
         is.corr=F,
         tl.col='black',
         tl.cex=0.8)
```
```{r}
## quality of representation of variables
## since PC1 to PC6 have the highest explained variance -- cos 2 elaborates that and the correlation between variables and Principal Components

corrplot(all_var_explained$cos2,
         is.corr=F,
         tl.col='black',
         tl.cex=0.8)
```

```{r}
## Contributions of variables to PC1 and PC2

library(gridExtra)

p1 = fviz_contrib(all_pca, choice="var", axes=1, fill="pink", top=10)

p2 = fviz_contrib(all_pca, choice="var", axes=2, fill="skyblue", top=10)

grid.arrange(p1,p2,ncol=2)
```

## 4. PC를 이용한 변수 클러스터링
```{r}
set.seed(21)

res_clusters = kmeans(all_var_explained$coord, centers=6, nstart=25) # nstart generates multiple initial configurations and reports the best one

groups = as.factor(res_clusters$cluster)


fviz_pca_var(all_pca,
             col.var = groups,
             palette="jco",
             legend.title="Cluster/PC",
             labelsize=6, repel=T) +
  theme(text=element_text(size=2, color="#002b80"),
        axis.title = element_text(size=3),
        axis.text = element_text(size=3)) +
  labs(title="Varibles clustered acc to Principal Component representation\n",
       x="Dim2 (19%)",
       y="Dim1 (44%)")
```
```{r}
## Biplot according to diagnosis

fviz_pca_biplot(all_pca, 
                col.ind = Cancer$Label_Diagnosis,
                col="#009999",
                palette="jco",
                legend.title = "Diagnosis",
                addEllipses=TRUE,
                geom="point", 
                repel=TRUE, # repel overlapping text
                labelsize=6) +
  theme(text = element_text(size = 2, color="#002b80"),
        axis.title = element_text(size = 5),
        axis.text = element_text(size = 5)) + 
  labs(title="Varibles clustered acc to Principal Component representation Segmented by Diagnosis\n",
    x="Dim2 (19%)",
    y="Dim1 (44%)")
```

<br><br><br>

## 5. 결론
PC1: Concavity, radius
PC2: radius, compactness, smoothness, fractal dimensions

```{r}
## Forming dataframe of the top 3 PCs and associated labels

pca = all_pca$x
pca = cbind(pca, Cancer)
pca = pca[,c(1:3, 31, 63)]

head(pca)
```
```{r}
table(pca$Label_Diagnosis)
```

### 5-1. PCA를 사용한 ML로 예측하기.
```{r}
# Splitting into training and test set using Caret package

library(caret)

set.seed(21)
train_index = createDataPartition(pca$Label_Diagnosis,
                                  p=0.8,
                                  list=F
                                  #times=1 # times: number of partitions to create
                                  )

train_df = pca[train_index,]
test_df = pca[-train_index,]
```

```{r}
dim(train_df)
```
```{r}
dim(test_df)
```

```{r}
## Almost similar proportion of benign to malignant in train and test set

prop.table(table(train_df$Label_Diagnosis))

prop.table(table(test_df$Label_Diagnosis))
```

```{r}
# C5.0 model

library(C50)

C50_model = C5.0(x=train_df[,1:3],
                 y=train_df$Label_Diagnosis,
                 ## Controlling overfitting,
                 control = C5.0Control(
                   earlyStopping = T, minCases = 10, CF=0.25),
                 trails=20)

# summary(c50_model)
# plot(c50_model)
```

```{r}
y_pred = predict(C50_model, test_df[,1:3])

cm_c5.0 = confusionMatrix(test_df$Label_Diagnosis, y_pred)


cm_c5.0
```

```{r}
acc_test <- numeric()
accuracy1 <- NULL; 
accuracy2 <- NULL

for(i in 1:50){
    C5.0_model_tuned <- C5.0(train_df[,1:3],train_df$Label_Diagnosis,trials = i)      
    y_pred <- predict(C5.0_model_tuned, test_df[,1:3]) 
    accuracy1 <- confusionMatrix(y_pred, test_df$Label_Diagnosis)
    accuracy2[i] <- accuracy1$overall[1]
}

acc <- data.frame(t= seq(1,50), cnt = accuracy2)

opt_t <- subset(acc, cnt==max(cnt))[1,]
sub <- paste("Optimal number of trials is", opt_t$t, "(accuracy :", opt_t$cnt,") in C5.0")


library(highcharter)
hchart(acc, 'line', hcaes(t, cnt)) %>%
  hc_title(text = "Accuracy With Varying Trials (C5.0)") %>%
  hc_subtitle(text = sub) %>%
  hc_add_theme(hc_theme_google()) %>%
  hc_xAxis(title = list(text = "Number of Trials")) %>%
  hc_yAxis(title = list(text = "Accuracy"))
```
```{r}
## After Tuning

c50_model <- C5.0(x= train_df[,1:3], 
                  y=train_df$Label_Diagnosis,
                  ## Controlling overfitting
                  conrol = C5.0Control(earlyStopping=TRUE, minCases=10, CF = 0.25),
                  trials=5
                 )

y_pred <- predict(c50_model, test_df[,1:3])
cm_c5.0 <- confusionMatrix(test_df$Label_Diagnosis, y_pred)
cm_c5.0
```
```{r}
## Adding final predictions to wbcd_df
test_df$Predicted_Diagnosis <- as.vector(y_pred)
head(test_df, 10)
```
```{r}
# Plotting confusion matrix

# par(mfrow=c(3,5))  # for making subplots
# #options(repr.plot.width = 1, repr.plot.height = 0.75)
# fourfoldplot(cm_c5.0$table, color=c("#CC6666", "#99CC99"), conf.level = 0, margin = 1, main = "C5.0 Confusion Matrix")
```

```{r}
library(randomForest)
train_df <- train_df
model_rf <- randomForest(train_df[,1:3], train_df$Label_Diagnosis, ntree=200, proximity=T, importance=T)
y_pred <- predict(model_rf, test_df[,1:3])
cm_rf <- confusionMatrix(test_df$Label_Diagnosis, y_pred)
cm_rf
```

